HO unification from object language to meta language

### 2024-03-19 paper/main.tex
update latex

@@

@@

\otext{The following goal: \elpiIn{X = lam x\ x, app[X, a] = a}}
\otext{We use links-beta}

>>>>

\newcommand{\linkbeta}{\texttt{link-}\ensuremath{\beta}\xspace}
\newcommand{\linketa}{\texttt{link-}\ensuremath{\eta}\xspace}

@@

Invarianti:
A destra della eta abbiamo sempre un termine che comincia per $\lambda x. bla$

La deduplicate eta:
  - viene chiamata che della forma [variable] -> [eta1] e [variable] -> [eta2] (a destra non c'è mai un termine con testa rigida)
  - i due termini a dx vengono unificati con la unif e uno dei due link viene buttato
    -> si mettono più lambda 
  - dopo l'unificazione rimane un link [variabile] -> [etaX] e quando
    risolviamo un eta-link, allora dobbiamo eta-espandere qb il termine di sinistra per
    poterlo  unifcare con quello di dx.

@@

The solution to this problem is to modify the compiler such that any sub-term $t$
considered as a potential $\beta$-redex is replaced with a hole $h$ and a new dedicated
link, called \linkbeta.

\begin{elpicode}
  type link-beta tm -> tm -> link.
\end{elpicode}

This link carries two terms, the former representing the variable $h$ for the
new created hole and the latter containing the subterm $t$. As for the \linketa,
we will call $h$ and $t$ respectively the left $lhs$ and the right $rhs$ hand
side of the \linkbeta.

At compile time, a subterm is \maybebeta, if it has the shape \elpiIn{fapp[fuva
N | L]} and \elpiIn{distinct L} does not hold. In that case, \elpiIn{L} is split
in two sublist \elpiIn{PF} and \elpiIn{NPF} such that former is the longest
prefix of \elpiIn{L} such that \elpiIn{distinct PF} holds. \elpiIn{NPF} is the
list such that \elpiIn{append PF NPF L}. The $lhs$ is set to a new variable
named $M$ with \elpiIn{PF} in scope whereas the $rhs$ is given by the term
\elpiIn{app[uva N' PF | NPF]} where the \Ho variable identified by \elpiIn{N'}
is mapped to the \Fo variable named \elpiIn{N}.

After its creation, a \linkbeta remain suspended until the head of $rhs$ is
instantiated by the oracle (see \cref{prop:simulation}). In this case, $rhs$ is
$\beta$-reduced to a new term, say $t'$. $t'$ is either a term in \llambda, in
which case $t'$ is unified with the $lhs$, otherwise, the link remain suspended
and no progress is performed. Another way to wake a \linkbeta up is when the
$lhs$ is a term \elpiIn{T} and $rhs$ has the shape \elpiIn{app[uva N PF | NPF]}
and some of the arguments in the \elpiIn{NPF} list become names. This is
possible after the resolution of other links. In this case, the list \elpiIn{L}
obtained by the concatenation between \elpiIn{PF} and \elpiIn{NPF} is split
again in to lists \elpiIn{PF'} and \elpiIn{NPF'}. If \elpiIn{PF} is not that
same as \elpiIn{PF'}, then we can 1) remove the current \linkbeta, 2) create a
new \linkbeta between \elpiIn{T} and \elpiIn{app[uva N' PF' | NPF']} and 3)
create a new \linketa between the variables \elpiIn{N} and \elpiIn{N'}.

An example justifying this last link manipulation is given by the following
unification problem:

\begin{elpicode}
  f = flam x\ flam y\ fapp[F, (X x), y] % $f = \lambda x.\lambda y.F (X x) y$
\end{elpicode}

\noindent
from the subsitution $\rho = \{X \mapsto \lambda x.x\}$.

\noindent
\otext{The following goal: \elpiIn{X = lam x\ x, app[X, a] = a}}
\otext{We use links-beta}
